---
title: "Towards a Predictive Model of Moral Concern"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
# Setup for targets:

library(targets)
tar_config_set(store = "_targets/")


# You can interact with tar objects as usual, e.g.:
# print(model)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/cjvanlissa/moral_standing.git>.

This is an example of a non-essential citation [@vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## Results

These are the Rsquared values on training and test data (use test data to determine unbiased performance estimates):

```{r}
temp_env <- new.env()
tar_load_everything(envir = temp_env)
res <- grep("res_", ls(envir = temp_env), value = TRUE)
tab_res <- temp_env$analysis_results$rsqs
rownames(tab_res) <- NULL
knitr::kable(tab_res, digits = 2)
```

The best performing model (or interpretable model whose cross-validated mean squared error was within 1SE of the best model's cross-validated mean squared error) is `r temp_env[["analysis_results"]][["best"]]`.

### Effect of Features and Model

The variance in model performance can be broken down into components due to model and feature set:

```{r}
tab_aov <- temp_env$analysis_results$etasqs
knitr::kable(tab_aov, digits = 2)
```

## Interpretation

```{r}
# dv = "cis4_nextwave"
# X <- model.matrix(as.formula(paste0(dv, "~.")), temp_env$dat$train)[, -1]
# Y <- as.numeric(temp_env$dat$train[[dv]])
# 
# sdx <- apply(X, 2, sd)
coefs <- as.numeric(glmnet:::coef.glmnet(temp_env$res_lasso$all$res, s = "lambda.1se"))
#coefs_sxy <- coefs
#coefs_sxy[-1] <- coefs[-1] * (sdx/sd(Y))

tab_coef <- data.frame(Predictor = c("Intercept", rownames(temp_env$res_lasso$all$res$beta)), b = coefs
                       #, beta = coefs_sxy
                       )

tab_coef <- tab_coef[order(abs(tab_coef$b), decreasing = T), , drop = F]
knitr::kable(tab_coef, caption = "LASSO regression coefficients.")
```
